Combinatorics of the geometry of Wilson loop diagrams II: Grassmann necklaces, dimensions, and denominators

### 2019-05-07 GWLDCII.tex

Let $W_r := (\cP_{in}(q_r),[n])$ be the subdiagram of $W$ consisting only of those propagators inside $q_r$ (including $q_r$ itself); in particular $W_r$ contains none of the previous $p_i$ or $q_i$. By the original hypotheses on $W$, every vertex in $[i_r,k_{r+1}]$ (which is a non-empty interval since $\ell(q_r) \geq 4$) must support at least one propagator. Therefore $W_r$ admits at least one propagator of length 2 (by Remark~\ref{rem:props of length 2 and 3}) and no propagators of length $3$ (by our assumption on $W$).

@@

Note that we could replace $q_r$ by another propagator $q'_{r}$ of length $\geq 4$ in $W_r$, as long as $p_{r+1}$ and $q_r$ are on opposite sides of $q_r'$, and such a new $q'_{r}$ would still satisfy all of the induction hypotheses. Therefore without loss of generality we may assume that $q_r$ has minimal length among propagators of length $\geq 4$ in $W_r$ which have $p_{r+1}$ on their inside.

@@

Note that since $j_{r+1}+4 \leq k_r-1$ in both of these situations, the vertex $j_{r+1}+4$ is inside $q_r$ but does not support either $q_r$ or $p_{r+1}$, and must therefore support some other propagator $t$.  Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and $W_r$ has no propagators of length 3, it follows that $\ell(t) \geq 4$.  If $q_r$ and $p_{r+1}$ were on different sides of $t$ then this would contradict the minimal length hypothesis on $q_r$.  Therefore we can orient $t$ so that all previous $q_i$ and $p_i$ belong to $\cP_{out}(t)$, and set $q_{r+1} = t$ to continue the induction.

>>>>

Let $W_r := (\cP_{in}(q_r),[n])$ be the subdiagram of $W$ consisting only of those propagators inside $q_r$ (including $q_r$ itself); in particular $W_r$ contains none of the previous $p_i$ or $q_i$. By the original hypotheses on $W$, every vertex in $[i_r,k_{r+1}]$ (of which there are at least 4, since $\ell(q_r) \geq 4$) must support at least one propagator. Therefore $W_r$ admits at least one propagator of length 2 (by Remark~\ref{rem:props of length 2 and 3}) and no propagators of length $3$ (by our assumption on $W$).

@@

Note that we could replace $q_r$ by another propagator $q'_{r}$ in $W_r$, as long as $p_{r+1}$ and $q_r$ are on opposite sides of $q_r'$: such a new $q'_{r}$ would still satisfy all of the induction hypotheses. Therefore without loss of generality we may assume that $q_r$ is the innermost propagator of length $\geq 4$ in $W_r$ which satisfies the induction hypotheses, i.e. we assume that there are no other propagators with $p_{r+1}$ on one side and $q_r$ on the other.

@@

Note that since $j_{r+1}+4 \leq k_r-1$ in both of these situations, the vertex $j_{r+1}+4$ is inside $q_r$ but does not support either $q_r$ or $p_{r+1}$, and must therefore support some other propagator $t$.  Since $p_{r+1}$ is not part of configuration \ref{item pair of 2s} and $W_r$ has no propagators of length 3, it follows that $\ell(t) \geq 4$.  If $q_r$ and $p_{r+1}$ were on different sides of $t$ then this would contradict the minimality of $q_r$.  Therefore we can orient $t$ so that all previous $q_i$ and $p_i$ belong to $\cP_{out}(t)$, and set $q_{r+1} = t$ to continue the induction.
